Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-11-15 manuscript.Rmd
fixat errorn som inte kan knitta fixat ny kod i main så att jag ger ut en noNA dataframe istället för två varierande för BE och SBP. ändrat i theisis texten kort för att prova att den nya noNA fungerar.

There were a total of `r nrow(merged.data)` patients in the trauma registry. Out of these, `r nrow(study.sample)` patients had been reviewed for the presence of opportunities for improvement. After exluding patients younger than 15 and/or were dead on arrival, `r nrow(study.sample)` patients remained. A total of X patients were finally excluded due to missing data, leaving us with Y patients for the final analysis.

@@

Sample characteristics are presented in Table \@ref(tab:sample-characteristics). A total of `r ofi` patients had at least one opportunity for improvement. The median age was `r age`. Most patients were male `r gender`.

@@

Report other analyses done—eg analyses of subgroups and interactions,
and sensitivity analyses 
-->
```
You can include code in this document like this:

>>>>

There were a total of `r merged` patients in the trauma registry. After excluding the patients younger than 15 and/or were dead on arrival, there were `r excludednum` patients left. Out of those, `r sample` patients had been reviewed for the presence of OFI. A total of `r sample - log_reg_countBE` patients were excluded for the BE classification group due to missing data, resulting in `r log_reg_countBE` patients for the final analysis. For the SBP group, missing data accounted for exclusion of `r sample - log_reg_countSBP` patients, leaving a sum of `r log_reg_countSBP` patients for the final analysis.

@@

Sample characteristics are presented in Table \@ref(tab:sample-characteristics). A total of `r ofi` patients had at least one opportunity for improvement. The median age was `r age`. Most patients were male `r male`.

@@

Report other analyses done—eg analyses of subgroups and interactions,
and sensitivity analyses

You can include code in this document like this:

### 2024-11-15 thesis.Rmd
fixat errorn som inte kan knitta fixat ny kod i main så att jag ger ut en noNA dataframe istället för två varierande för BE och SBP. ändrat i theisis texten kort för att prova att den nya noNA fungerar.

## Participants
There were a total of `r merged` patients in the trauma registry. After excluding the patients younger than 15 and/or were dead on arrival, there were `r excludednum` patients left. Out of those, `r sample` patients had been reviewed for the presence of OFI. A total of `r sample - log_reg_countBE` patients were excluded for the BE classification group due to missing data, resulting in `r log_reg_countBE` patients for the final analysis. For the SBP group, missing data accounted for exclusion of `r sample - log_reg_countSBP` patients, leaving a sum of `r log_reg_countSBP` patients for the final analysis.

@@

```{r sample-characteristics SBP, echo=FALSE}
sample.characteristics.tableSBP
```

>>>>

## Participants
There were a total of `r merged` patients in the trauma registry. After excluding the patients younger than 15 and/or were dead on arrival, there were `r excludednum` patients left. Out of those, `r sample` patients had been reviewed for the presence of OFI. A total of `r sample - log_reg_count` patients were excluded due to missing data, resulting in `r log_reg_count` patients for the final analysis.

@@
